---
title: Data Visualization-Scatter Plots
author: Ronald Bonavita
date: '2017-09-27'
slug: data-visualization-scatter-plots
categories:
  - R
  - Scatter Plots
  - Visualization
tags:
  - Visualization
  - Scatter Plots
---
```{r warning=FALSE, message=FALSE}
library(Lahman)
library(sqldf)
library(ggplot2)
```

There will be times when working in Data Science where you will want to visualize the output of your data. In the 9:00am session of MIS 150, we worked on making scatter plots in RStudio, running a query searching for players with at least 400 career homeruns.
```{r}
#Extractcing Data----------------------------

query<-"SELECT playerID,sum(HR) AS career_HR ,sum(SO) AS career_SO 
FROM Batting
GROUP BY playerID
HAVING sum(HR)>=400"

result<-sqldf(query)

#Visulaizing Data----------------------------

ggplot()+
  geom_point(data=result,aes(x=career_SO,y=career_HR), size=3, color="blue")+
  ggtitle("Career Strikeouts vs. Homeruns for Great Hitters")+
  xlab("Career Strikeouts")+
  ylab("Career Homeruns")
```

As you can see above, we assigned the output of the query to the variable 'result', storing it for later use. We then ran the syntax to make a scatter plot with Career Strikeouts at the X-Axis and Career Homeruns as the Y-Axis, as well as using size 3 blue points.